INFOMDA2: Group Assignment

### 2025-01-15 code/analysis.qmd
update analysis

Even though we have reduced the number of variables to `r nrow(sig_001)`, the algorithm still does not seem to converge. In the li

@@

```{r}
logit_7 <- data_pca %>% 
  select(pc1, pc2, pc3, pc4, pc5, pc6, pc7, class) %>%
  train(
    class ~ .,
    data = .,
    method = "glm",
    family = "binomial",
    trControl = trainControl(method = "cv", number = 10)
  )

summary(logit_7)
logit_7$results
```

>>>>

Even though we have reduced the number of variables to `r nrow(sig_001)`, the algorithm still does not seem to converge. The issue here

@@

### Iteratively Add Components

```{r}
logit_results <- rep(NA, length(pc_greaterthan1))

for (i in 1:length(pc_greaterthan1)) {
  logit <- data_pca %>% 
    select(all_of(pc_greaterthan1[1:i]), class) %>%
    train(
      class ~ .,
      data = .,
      method = "glm",
      family = "binomial",
      trControl = trainControl(method = "LOOCV")
    )

  logit_results[i] <- logit$results$Accuracy

}

ggplot(data = data.frame(x = 1:length(pc_greaterthan1), y = logit_results), aes(x = x, y = y)) +
  geom_line() +
  labs(x = "Number of Components", y = "Accuracy", title = "Accuracy by Number of Components") +
  theme_minimal()
```

Only keep components that increase accuracy

```{r}
diff <- c(0, diff(logit_results))

index <- which(diff >= 0)
```

```{r}
logit_results_incr <- rep(NA, length(index))

for (i in seq_along(index)) {
  logit <- data_pca %>% 
    select(all_of(pc_greaterthan1[index[1:i]]), class) %>%
    train(
      class ~ .,
      data = .,
      method = "glm",
      family = "binomial",
      trControl = trainControl(method = "LOOCV")
    )

  logit_results_incr[i] <- logit$results$Accuracy

}

diff_incr <- c(0, diff(logit_results_incr))

index_incr <- index[which(diff_incr >= 0)]

logit_results_incr2 <- rep(NA, length(index_incr))

for (i in seq_along(index_incr)) {
  logit <- data_pca %>% 
    select(all_of(pc_greaterthan1[index_incr[1:i]]), class) %>%
    train(
      class ~ .,
      data = .,
      method = "glm",
      family = "binomial",
      trControl = trainControl(method = "LOOCV")
    )

  logit_results_incr2[i] <- logit$results$Accuracy

}

diff_incr2 <- c(0, diff(logit_results_incr2))

index_incr2 <- index_incr[which(diff_incr2 >= 0)]

logit_results_incr3 <- rep(NA, length(index_incr2))

for (i in seq_along(index_incr2)) {
  logit <- data_pca %>% 
    select(all_of(pc_greaterthan1[index_incr[1:i]]), class) %>%
    train(
      class ~ .,
      data = .,
      method = "glm",
      family = "binomial",
      trControl = trainControl(method = "LOOCV")
    )

  logit_results_incr3[i] <- logit$results$Accuracy

}
```

```{r}
iterations <- 10

# Initialize index_incr for the first iteration
index_incr <- index

# Store results of each iteration
logit_results_all <- list()
diff_results_all <- list()

for (iteration in 1:iterations) {

  logit_results <- rep(NA, length(index_incr))

  for (i in seq_along(index_incr)) {
    logit <- data_pca %>% 
      select(all_of(pc_greaterthan1[index_incr[1:i]]), class) %>%
      train(
        class ~ .,
        data = .,
        method = "glm",
        family = "binomial",
        trControl = trainControl(method = "LOOCV")
      )

    logit_results[i] <- logit$results$Accuracy
  }

  diff_results <- c(0, diff(logit_results))

  # Save results of the current iteration
  logit_results_all[[iteration]] <- logit_results
  diff_results_all[[iteration]] <- diff_results

  # Update index_incr for the next iteration
  index_incr <- index_incr[which(diff_results >= 0)]

  # Break the loop if no more indices are selected
  if (length(index_incr) == 0) break
}

# Final result stored in logit_results_all and diff_results_all for all iterations

```

```{r}
ggplot(data = data.frame(x = 1:length(index_incr), y = logit_results_all[[10]]), aes(x = x, y = y)) +
  geom_line() +
  labs(x = "Number of Components", y = "Accuracy", title = "Accuracy by Number of Components") +
  theme_minimal()
```

```{r}
logit <- data_pca %>% 
      select(all_of(pc_greaterthan1[index_incr]), class) %>%
      train(
        class ~ .,
        data = .,
        method = "glm",
        family = "binomial",
        trControl = trainControl(method = "LOOCV")
      )

summary(logit)
```
